Machine Learning for Handwriting Recognition: Algorithms and Techniques

### 2023-10-30 Manuscript/main.tex
Added Keywords
Added Paragraph of Data Collections

@@

\paragraph{Paragraph 1}

\paragraph{Paragraph 2}

\paragraph{Paragraph 3}

>>>>

\paragraph{Abstract}
Will be Implemented after the article is finished.

\paragraph{Keywords}
Machine Learning, Deep Learning, Handwriting Recognition, Activation Function, Model, Parameters...

@@

\paragraph{Data Collection}
In tackling handwriting recognition tasks, selecting the right libraries and packages is paramount for achieving robust training results. Noteworthy libraries include TensorFlow and Keras which offer a plethora of deep learning functionalities crucial for building and training neural networks adept at recognizing handwritten characters. Additionally, PyTorch is a highly flexible and dynamic open-source machine learning framework that is particularly known for its ease of use and suitability for a variety of tasks, including handwriting recognition. It allows for the construction, training, and evaluation of deep neural networks with a straightforward and Pythonic interface.On the other hand, the MNIST dataset is a classic in the machine learning community, comprising 60,000 training images and 10,000 testing images of handwritten digits from 0 to 9. Each image is grayscale and 28x28 pixels in size. This dataset has been widely used as a benchmark to evaluate and compare different algorithms' performance in the domain of handwriting recognition. When utilized in conjunction with PyTorch, the MNIST dataset can serve as a powerful tool to develop and evaluate handwriting recognition models efficiently. 
\paragraph{Paragraph 3}
